---
title: "Descriptive Statistics"
author: "Bin & Lizzy"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    toc_depth: 6
    code_folding: hide
---

```{r, include = FALSE}
library(tidyverse)
library(here)

PREPOST_PATH <- here("data/processed/prepost_cleaned_w_std_lrn_gain.csv")
REPLICATE_PATH <- here("data/processed/replicate.csv")
EVENODD_PATH <- here("data/processed/even_odd_metrics.csv")

df_prepost <- read_csv(PREPOST_PATH)
df_replicate <- read_csv(REPLICATE_PATH)
df_evenodd <- read_csv(EVENODD_PATH)
```
### CK_pre, CK_post, PK-diagram_pre, PK-diagram_post, PK-nodiagram_pre, PK-nodiagram_post

```{r}
df_prepost %>%
  select(CK_pre, CK_post, PK_diagram_pre, PK_diagrm_post, PK_nodiagram_pre, PK_nodiagram_post) %>%
  gather() %>%
  group_by(key) %>%
  summarise(Mean = mean(value),
            `Standard Deviation` = sd(value)) %>%
  rename("Component" = key)
```


### Overall average hint per step, time spent, and average incorrect (symbolic steps only)

+ Cannot do time spent per symbolic step because don't have it calculated (used the old transaction data with weird values of durations)
+ *The time calculation here is completely different from that for the even/odd analysis*
+ No one used hints on diagrammic steps (so symbolic steps only is the same for overall)

```{r}
df_replicate %>%
  select(avg_hints_sym, adj_avg_tps, avg_inc_sym) %>%
  rename(`Avg. Time Per Step` = adj_avg_tps,
         `Avg. Hint Used per Symbolic Steps` = avg_hints_sym,
         `Avg. Incorrects per Symbolic Step` = avg_inc_sym) %>%
  gather() %>%
  group_by(key) %>%
  summarise(Mean = mean(value),
            `Standard Deviation` = sd(value)) %>%
  rename("Component" = key)
```

### Average hint per step, time spent, and average incorrect (symbolic steps only) for **odd** problems

```{r}
df_evenodd %>%
  filter(group %in% c("odd_dia", "odd_int")) %>%
  select(avg_hints_sym, avg_tps_sym, avg_inc_sym) %>%
  rename(`Avg. Time Per Step` = avg_tps_sym,
         `Avg. Hint Used per Symbolic Steps` = avg_hints_sym,
         `Avg. Incorrects per Symbolic Step` = avg_inc_sym) %>%
  gather() %>%
  group_by(key) %>%
  summarise(Mean = mean(value),
            `Standard Deviation` = sd(value)) %>%
  rename("Component" = key)
```

### Average hint per step, time spent, and average incorrect (symbolic steps only) for **even** problems


```{r}
df_evenodd %>%
  filter(group %in% c("eve_dia", "eve_int")) %>%
  select(avg_hints_sym, avg_tps_sym, avg_inc_sym) %>%
  rename(`Avg. Time Per Step` = avg_tps_sym,
         `Avg. Hint Used per Symbolic Steps` = avg_hints_sym,
         `Avg. Incorrects per Symbolic Step` = avg_inc_sym) %>%
  gather() %>%
  group_by(key) %>%
  summarise(Mean = mean(value),
            `Standard Deviation` = sd(value)) %>%
  rename("Component" = key)
```